Hydra Battles and Cie

### 2021-05-20 doc/chapter-primrec.tex
more transparent proofs of predicate isPR

\section{Proving that a given function is \emph{not} primitive recursive}
\label{sect:ack-not-PR}

@@

\subsection{The length of standard hydra battles}

@@

\subsubsection{Definitions}

@@

\subsubsection{Proof steps}

@@

\begin{Coqsrc}
Section battle_lenght_notPR.

@@

\begin{Coqsrc}
Let alpha := Phi0 omega%e0.
Let h := iota (cnf alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
Let m k := L_ alpha (S k).

Remark m_eqn : forall k, m k = (l_std alpha k + k)%nat.
(* ... *)
\end{Coqsrc}

@@

\emph{Please note that our proof of this lemma is not trivial at all. It uses some lemmas of Chapters~\vref{chap:ketonen} and \vref{chap:alpha-large}.}

@@

\begin{Coqsrc}
H_L_ : forall (alpha : E0) (i : nat), H_ alpha i <= L_ alpha (S i)
\end{Coqsrc}

@@

\begin{Coqsrc}
F_vs_Ack : forall n : nat, 2 <= n -> Ack n n <= F_ omega n
\end{Coqsrc}

@@

End battle_lenght_notPR.
\end{Coqsrc}

>>>>

\section{Ackermann: a non  primitive recursive function}
\label{sect:ack-not-PR}

@@

\section{The length of standard hydra battles}

@@

\subsection{Definitions}

@@

\subsection{Main proof steps}

@@

\begin{Coqsrc}
Section battle_length_notPR.

@@

\begin{Coqsrc}
Let delta := Phi0 omega%e0.
Let h := iota (cnf delta).
\end{Coqsrc}

@@

\begin{Coqsrc}
Let m k := L_ delta (S k).

Remark m_eqn : forall k, m k = (l_std delta k + k)%nat.
(* ... *)
\end{Coqsrc}

@@

\emph{Please note that our proof of this lemma is not trivial at all. It uses some lemmas of Chapters~\vref{chap:ketonen} and \vref{chap:alpha-large}. Mainly:}

\begin{Coqanswer}
H'_restricted_mono_l:
  forall (alpha beta : E0) (n : nat),
  Canon_plus n alpha beta -> H'_ beta n <= H'_ alpha n
\end{Coqanswer}

This lemma is proven in 
\href{../theories/html/hydras.Epsilon0.Hprime.html}{Epsilon0.Hprime}, with the help of the \emph{Ketonen-Solovay machinery}.

@@

\begin{Coqsrc}
H'_L_: forall (alpha : E0) (i : nat), 
      H'_ alpha i <= L_ alpha (S i)
\end{Coqsrc}

@@

\begin{Coqsrc}
F_vs_Ack: forall n : nat, 2 <= n -> Ack n n <= F_ omega n
\end{Coqsrc}

@@

End battle_length_notPR.
\end{Coqsrc}
